# Citing Figures, Tables & Sections {#sec-start}

When you're writing a report, you often refer to a table or figure in text. 

```{r}
#| label: no-show
#| include: false
#| message: false
gapminder <- readr::read_csv(here::here("data", "gapminder.csv"))
```

> Australia's life expectancy has increased a great deal over the past 50 years (Figure 1)

```{r}
#| label: example-gg-oz-gap
#| echo: false
#| message: false
library(ggplot2)
library(dplyr)
gapminder %>%
  filter(country == "Australia") %>%
  ggplot(aes(x = year,
             y = lifeExp)) + 
  geom_point()
```

_Figure 1. Life expectancy from 1952 - 2007 for Australia. Life expectancy increases steadily except from 1962 to 1969. We can safely say that our life expectancy is higher than it has ever been!_

And sure, this is figure 1...for now.

But what happens if actually, that figure should be moved later in the paper?

You need to do the following:

1. Update the reference to figure 1 in the text. 
1. Update the figure 1 caption to not say figure 1.

This is fine. 

Once. 

But it is __never__ once. After this, it is frustrating, and error prone.

There is a way to solve this, using figure citations, which this lesson discusses.

## Overview

* **Teaching** 10 minutes
* **Exercises** 15 minutes

## Questions

* How do I refer to the table or figure in text and link to it?

## Objectives

* Link to tables or figures in text.

## How to refer to tables and figures in text? (demo)

- Tables are referenced in text with `@tbl-label`
- Figures are references in text with `@fig-label`

Importantly here, for these two above examples to work, the things that they are referring to must have the exact label `tbl-label` and `fig-label`, respectively. That is, they must have the `tbl` or the `fig` part in there!

So, in order to use this referencing style, you must use specific labelling of your code chunks. For example, if you have some code like this:

```{r}
#| echo: fenced
#| label: example-figure
image(volcano)
```

Then you cannot reference this figure in text - `@example-figure` does not work: @example-figure. We get the error: "example-figure?".

It would need to have a label like:

```{r}
#| echo: fenced
#| label: fig-example
image(volcano)
```

Then you can reference it with: `@fig-example` - @fig-example.

::: {.callout-tip title="Hover your mouse on a figure!"}
Note the awesome on-hover behaviour for hovering over a reference!
:::

Also note that there are a variety of ways to specify the figure:

- `@fig-example`: @fig-example
- `@Fig-example`: @Fig-example
- `[Fig @fig-example]`: [Fig @fig-example]
- `-@fig-example`: Figure -@fig-example

(reference here: <https://quarto.org/docs/authoring/cross-references.html#references>)

:::{.callout-note title="Your Turn"}

1. Using "03-qmd-lm-tables-inline-qmd"
    1. Convert your output to use `fig` prefixes to reference figures

:::

:::{.callout-tip title="Demo"}

```{r}
#| label: fig-gg-oz
#| echo: fenced
#| fig-cap: Life expectancy from 1952 - 2007 for Australia. Life expectancy increases
#|   steadily except from 1962 to 1969. We can safely say our life expectancy is
#|   higher than it has ever been!
library(ggplot2)
library(dplyr)
gapminder %>%
  filter(country == "Australia") %>%
  ggplot(aes(x = year,
             y = lifeExp)) + 
  geom_point()
```

Australia's life expectancy has increased a great deal over the past 50 years (See Figure -@fig-gg-oz).

:::

:::{.callout-note title="Your Turn"}

1. Using "03-qmd-lm-tables-inline-qmd":
    1. Add a new plot in your document and reference it

:::

## Referencing a table

To cite a table, you write the following:

`@tbl-chunk-name`

```{r}
#| label: tbl-gg-oz-tab
#| echo: fenced
gapminder %>%
  filter(country == "Australia") %>%
  knitr::kable(caption = "Raw gapminder data for Australia.")
```

See above in Table @tbl-tbl-gg-oz-tab.

If you want to move the caption location you can use `tbl-cap-location: <position>` to specify the location. By default it is the top.

```{r}
#| label: tbl-gg-oz-tab-bottom
#| tbl-cap-location: bottom
#| echo: fenced
gapminder %>%
  filter(country == "Australia") %>%
  knitr::kable(caption = "Raw gapminder data for Australia.")
```

Reference: <https://quarto.org/docs/authoring/cross-references.html#tables> and <https://quarto.org/docs/authoring/tables.html#caption-location>

## Other things you can cross/reference

You can also reference theorems, code, proofs, and equations! See <https://quarto.org/docs/authoring/cross-references.html#theorems-and-proofs> for more details.

:::{.callout-note title="Your Turn"}

1. Using "03-qmd-lm-tables-inline-qmd"
    1. Create a table in your document and refer to it in text

:::

## Referencing a section

You can even reference a section in your report: `@sec-slug`

However, in order to write this, you need to include `sec-slug` in your markdown header, like so:

```
## your amazing header {#sec-slug}
```

You must also include `number-section` in your YAML:

```r
---
title: "example"
number-sections: true
---
```

For example, I can refer to the first section (Section @sec-start) in this document by referring to the section as 

`(Section @sec-start)`

because it was written as:

```
# Citing Figures, Tables & Sections {#sec-start}
```


:::{.callout-tip title="Demo: Using visual mode"}

Visual mode is this pretty neat feature, it's best demonstrated live!

:::

:::{.callout-note title="Your Turn"}

1. Using "03-qmd-lm-tables-inline-qmd"
    1. Reference a section in the report.
1. Open up "04-qmd-global-opts-device.qmd" and work through the tasks there

:::
