# Installation

In this section, the aim is to have everyone setup with R, RStudio, and quarto

## Overview

* **Duration** 15 minutes

## Questions

* How do I install R?
* How do I install quarto?
* How do I install LaTeX in a sane way?

## Software Setup

### R

#### Windows

https://cloud.r-project.org/bin/windows/

#### MacOS

https://cloud.r-project.org/bin/macosx/

#### Linux

https://cloud.r-project.org/bin/linux/

### RStudio

https://www.rstudio.com/products/rstudio/download/#download

## quarto

To ensure you are up to date, run the following script to install the packages.

```{r}
#| label: install-rmd
#| eval: false
install.packages("quarto")
install.packages("knitr")
install.packages("here")
install.packages("tidyverse")
install.packages("broom")
install.packages("fs")
install.packages("usethis")
```

## A note on PDF

quarto documents can be compiled to PDF, which is a great feature. In order to convert the documents to PDF, they use a software called LaTeX (\LaTeX) (pronounced la-tek or lay-tek). 

Installing LaTeX is thankfully handled when you install quarto, as [quarto includes a built-in Latexmk engine](https://quarto.org/docs/output-formats/pdf-engine.html#latexmk).

## Test Script

You should be able to run the following code on your machine

```{r}
#| label: library-test
#| eval: false
library(quarto)
library(knitr)
library(here)
library(tidyverse)
library(broom)
library(fs)
library(usethis)
```
