# Installation

In this section, the aim is to have everyone setup with R, RStudio, and Quarto

## Overview

* **Duration** 15 minutes

## Questions

* How do I install R?
* How do I install Quarto?
* How do I install LaTeX in a sane way?

## Software Setup

### R

#### Windows

[https://cloud.r-project.org/bin/windows/](https://cloud.r-project.org/bin/windows/)

#### MacOS

[https://cloud.r-project.org/bin/macosx/](https://cloud.r-project.org/bin/macosx/)

#### Linux

[https://cloud.r-project.org/bin/linux/](https://cloud.r-project.org/bin/linux/)

### RStudio

[https://posit.co/download/rstudio-desktop/#download](https://posit.co/download/rstudio-desktop/#download)

### Quarto

[Quarto installation page](https://quarto.org/docs/get-started/)

## Checking you are up to date

To ensure you are up to date, run the following script to install the packages.

```{r}
#| label: install-rmd
#| eval: false
install.packages("quarto")
install.packages("knitr")
install.packages("here")
install.packages("tidyverse")
install.packages("broom")
install.packages("fs")
install.packages("usethis")
```

## A note on PDF

Quarto documents can be compiled to PDF, which is a great feature. In order to convert the documents to PDF, they use a software called [LaTeX](https://www.latex-project.org/) (pronounced la-tek or lay-tek).

Installing LaTeX is thankfully handled when you install Quarto, as [Quarto includes a built-in Latexmk engine](https://quarto.org/docs/output-formats/pdf-engine.html#latexmk). 

### PDF / LaTeX Pain

Installing LaTeX [can be a pain](https://yihui.name/tinytex/pain/), but thankfully Yihui Xie has put a lot of time and energy into making an easier way to install it - [`tinytex`](https://yihui.name/tinytex/). `tinytex` is an R package that installs a sane, lightweight (<200Mb) version of LaTeX. 

If you are running into issues rendering a PDF, you can try the following:

```{r}
#| label: run-tiny-tex
#| eval: false
tinytex::install_tinytex()
```

If you get the following error, **this is good**! As it means that TeX has already been installed:

```
Error: Detected an existing tlmgr at /usr/local/bin/tlmgr. It seems TeX Live has been installed (check tinytex::tinytex_root()). You have to uninstall it, or use install_tinytex(force = TRUE) if you are sure TinyTeX can override it (e.g., you are a PATH expert or installed TinyTeX previously).
```

Alternatively, you can run the following from the terminal

```{shell}
#| eval: false
quarto install tinytex
# follow the prompts from here
```

### Problem solving with LaTeX

If you have any problems with installing `tinytex`, I recommend you check out the [tinytex FAQ page](https://yihui.name/tinytex/faq/).

## Test Script

You should be able to run the following code on your machine

```{r}
#| label: library-test
#| eval: false
library(quarto)
library(knitr)
library(here)
library(tidyverse)
library(broom)
library(fs)
library(usethis)
```
